Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2012-02-03 ms.tex
Updated figure 4 and 5 captions

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
(arrows with different grey scales), assuming
that $\alpha=2.3$ except in the 1--3 GeV energy interval where $\alpha=2.1$ is adopted. These are
compared to integrated spectra of the same energy interval and aperture, assuming the universal
gamma-ray spectrum of clusters \citep[lines with different grey
scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
\label{fig:spectrum}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f5.eps}}
\end{center}
\caption{CR-to-thermal pressure, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as a
function of radial distance from the center of the Coma. Model predictions are shown by dashed
lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most constraining
VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within 0.4$^\circ$
(dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
$X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (black) which we use to
compare to the upper limits.}
\label{fig:xcr}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f4.eps}}
\end{center}
\caption{Integral gamma-ray flux upper limits for \Fermi and VERITAS observations of the Coma
cluster (given in Tables~\ref{table:results} and \ref{table:fermi}) for different integration radii
(arrows with different grey scales), assuming that $\alpha=2.3$ except in the 1--3 GeV energy
interval where $\alpha=2.1$ is adopted. $R_{\rmn{vir}}$ is the virial radius of the Coma cluster.
These are compared to integrated spectra of the same energy interval and aperture, assuming the
universal gamma-ray spectrum of clusters \citep[lines with different grey
scales,][]{article:PinzkePfrommer:2010}.To guide the eye, we show the underlying universal integral
energy distribution of pion decay gamma-rays, $E_\gamma F_\gamma(>E_\gamma)$, resulting from hadronic
interactions of CRs and ICM protons (dotted). For visualization purposes all photon fluxes are
weighted with the smallest energy in each interval. Note that the \Fermi limit for the energy
interval of 1--3 GeV within the aperture of 0.4$^\circ$ is most constraining.}
\label{fig:spectrum}
\end{figure*}

\begin{figure*}
\begin{center}
\scalebox{1.0}{\plotone{f5.eps}}
\end{center}
\caption{CR-to-thermal pressure ratio, $X_{\mathrm{CR}}=\expval{P_{\CR}}/ \expval{P_{\mathrm{th}}}$, as
a function of radial distance from the center of the Coma cluster. Model predictions are shown by
dashed lines \citep{article:PinzkePfrommer:2010} while these are scaled to match the most
constraining VERITAS upper limits within 0.2$^\circ$ (solid) and \Fermi upper limits within
0.4$^\circ$ (dashed). We compare differential $X_\CR$-profiles (grey) to integrated profiles
$X_{\CR}(<R/R_{\rmn{vir}})=\int_0^R P_\CR\, dV / \int_0^R P_{\rmn{th}}\, dV$ (black) which we use to
compare to the upper limits.}
\label{fig:xcr}
\end{figure*}
